\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{array}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage{longtable}
\usepackage{tabularx}

\geometry{margin=2.4cm}
\setlist[itemize]{leftmargin=1.4em,itemsep=0.25em,topsep=0.35em}
\setlist[enumerate]{leftmargin=1.6em,itemsep=0.25em,topsep=0.35em}

\renewcommand{\arraystretch}{1.25}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.65em}

\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}p{0.65cm}}

\newcommand{\fillline}[1]{\makebox[#1][l]{\hrulefill}}
\newcommand{\ansline}{\par\noindent\rule{\linewidth}{0.3pt}\par\vspace{0.5em}}
\newcommand{\ansblock}{\ansline\ansline}

\title{Checkly --- User Acceptance Testing Survey\vspace{0.3em}\\\large Draft v1 --- Survey Instrument}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Note to the Team}

\textit{Delete this section before sending the survey out.}

\begin{enumerate}
  \item Fill in the placeholders in brackets (app link, test account / sample PDF, deadline, contact email).
  \item Decide on a sending format: paste the questions into Google Forms / Typeform, or send this document as a fillable PDF.
  \item Aim for \textbf{at least 5 participants} who plausibly match our target user (someone who does recurring inspections, audits, QA checks, or checklist-based work --- e.g.\ a safety officer, facility/maintenance technician, QA engineer, or site supervisor). A less perfect proxy, such as a teammate or another student, is acceptable as a backup but should be noted as such in the report.
  \item Everything from the next section onward is what participants actually see.
\end{enumerate}

\section*{Introduction}

Thank you for taking the time to try out \textbf{Checkly}!

Checkly is an AI-assisted checklist tool: you design a checklist (e.g.\ a safety inspection, equipment check, or quality audit), optionally attach reference documents (PDFs) for context, and then fill it out --- verifying items with photos and an AI assistant that can help you build and check off the form by chatting with it.

We are building this as part of a university project and would love your honest feedback --- including the negative kind. It helps us much more than compliments.

\textbf{Time required:} approximately 15--20 minutes.\\
\textbf{What you'll do:} try a few core tasks in the app, then answer some short questions.\\
\textbf{Privacy:} your responses will only be used for this course project's evaluation. You can skip your name/email if you prefer to stay anonymous.

\textbf{App link:} \url{https://checkly-builder.vercel.app/}\\
\textbf{Test account / login (if needed):} [INSERT CREDENTIALS]\\
\textbf{Sample PDF to upload during the task} (if you don't have your own): [INSERT LINK TO SAMPLE PDF, e.g.\ a short safety-guideline or manual]\\
\textbf{Please complete this by:} [INSERT DEADLINE]

If you get stuck or something breaks, please note it down anyway in the feedback section --- that is valuable too.

\section*{Part 1 --- About You}

\begin{enumerate}
  \item Name \textit{(optional)} \fillline{6cm}
  \item Email \textit{(optional --- only if you're open to a short follow-up question)}\\
  \fillline{6cm}
  \item What is your current role / occupation? \fillline{6cm}
  \item Does your work or studies involve recurring inspections, audits, quality checks, or checklist-based tasks (e.g.\ safety inspections, equipment/maintenance checks, site audits, QA checklists)?\\
  $\Box$ Yes \qquad $\Box$ No
  \item If yes, briefly describe what kind: \fillline{8cm}
  \item What do you currently use to manage these checklists/inspections?
  \begin{itemize}[label=$\Box$]
    \item Paper forms
    \item Excel / Google Sheets
    \item Word / PDF templates
    \item Dedicated inspection software (please name it: \fillline{4cm})
    \item Nothing formal
    \item Other: \fillline{5cm}
  \end{itemize}
  \item How comfortable are you with learning new software/apps in general?
  \begin{center}
  \begin{tabular}{*{5}{c}}
  1 & 2 & 3 & 4 & 5\\
  $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
  \end{tabular}\\[0.2em]
  {\small (1 = Not comfortable, 5 = Very comfortable)}
  \end{center}
\end{enumerate}

\section*{Part 2 --- Try Checkly}

Please complete these steps in order. Don't worry about doing it ``perfectly'' --- we want to see how it feels for a first-time user.

\begin{enumerate}
  \item \textbf{Sign up / log in} at \url{https://checkly-builder.vercel.app/}.
  \item \textbf{Create a new checklist} --- give it a title and description (e.g.\ ``Safety inspection --- Warehouse A'').
  \item \textbf{Upload a PDF as context} for the checklist (use the sample PDF above, or one of your own, e.g.\ a guideline/manual).
  \item \textbf{Build out the checklist}: add at least one section, and a mix of item types (e.g.\ a checkbox, a text field, and a photo-check item).
  \item \textbf{Open the AI Assistant} and ask it to do at least one thing for you --- e.g.\ ``Add a section for fire safety with two checkbox items'' or ``What does this checklist cover?''
  \item \textbf{Run through the checklist} as if performing the inspection: check off a few items, fill in a text field, and upload at least one photo as evidence.
  \item \textbf{Go to the dashboard} and check your progress / stats for the checklist you created.
  \item \textbf{Export the checklist to PDF} using the ``Create PDF'' option.
\end{enumerate}

\section*{Part 3 --- Evaluation}

\textit{Rate each statement from 1 (Strongly disagree) to 5 (Strongly agree).}

\subsection*{3.1 First impression \& onboarding}

\begin{tabularx}{\textwidth}{@{}YCCCCC@{}}
\toprule
Statement & 1 & 2 & 3 & 4 & 5\\
\midrule
It was easy to understand what Checkly does within the first minute. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
I knew what to do without needing outside instructions. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
The interface felt clear and uncluttered. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
\bottomrule
\end{tabularx}

\subsection*{3.2 Creating a checklist \& PDF context}

\begin{tabularx}{\textwidth}{@{}YCCCCC@{}}
\toprule
Statement & 1 & 2 & 3 & 4 & 5\\
\midrule
Creating a new checklist was straightforward. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
Attaching a PDF as context felt useful, not just an extra step. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
Adding sections and different item types (checkbox, text, photo, etc.) was intuitive. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
\bottomrule
\end{tabularx}

\subsection*{3.3 AI Assistant}

\begin{tabularx}{\textwidth}{@{}YCCCCC@{}}
\toprule
Statement & 1 & 2 & 3 & 4 & 5\\
\midrule
The AI Assistant understood what I asked it to do. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
The changes the AI made matched what I expected. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
I trusted the AI Assistant's changes to my checklist. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
The AI Assistant saved me time compared to doing it manually. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
\bottomrule
\end{tabularx}

\subsection*{3.4 Photo verification}

\begin{tabularx}{\textwidth}{@{}YCCCCC@{}}
\toprule
Statement & 1 & 2 & 3 & 4 & 5\\
\midrule
Uploading a photo as proof for a checklist item was easy. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
I see clear value in photo verification for real inspections. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
\bottomrule
\end{tabularx}

\subsection*{3.5 Dashboard \& progress tracking}

\begin{tabularx}{\textwidth}{@{}YCCCCC@{}}
\toprule
Statement & 1 & 2 & 3 & 4 & 5\\
\midrule
The dashboard gave me a clear sense of progress/status. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
The PDF export would be useful for sharing/reporting results. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
\bottomrule
\end{tabularx}

\subsection*{3.6 Overall}

\begin{tabularx}{\textwidth}{@{}YCCCCC@{}}
\toprule
Statement & 1 & 2 & 3 & 4 & 5\\
\midrule
Checkly would solve a real problem I (or someone in my field) have today. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
I would consider using Checkly (or recommending it) for real inspection/checklist work. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
Overall, I am satisfied with my experience using Checkly. & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
\bottomrule
\end{tabularx}

\subsection*{Likelihood to recommend}

On a scale of 0--10, how likely are you to recommend Checkly to a colleague who does this kind of work?

\begin{center}
\begin{tabular}{*{11}{c}}
0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10\\
$\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$ & $\Box$\\
\end{tabular}
\end{center}

\section*{Part 4 --- Open Feedback}

\begin{enumerate}
  \item What did you like most about Checkly?
  \ansblock
  \item What was confusing, slow, or didn't work as you expected?
  \ansblock
  \item If you could change or add one thing, what would it be?
  \ansblock
  \item Is there a feature you expected to find but didn't?
  \ansblock
  \item Any other comments?
  \ansblock
\end{enumerate}

\section*{Closing}

Thank you so much for your time --- this directly shapes what we build next!

\textit{Questions about this survey? Contact: [INSERT CONTACT EMAIL]}

\end{document}
